A novel distributed nature-inspired algorithm for solving optimization problems\thanks{Supported by TECNOLÓGICO NACIONAL DE MÉXICO (TecNM).}

### 2021-09-29 paper.tex
Work in progress
Minor text improvement.

Experiment 3: The goal of our third experiment was to follow and study the
behavior of the Life-Cycle algorithm that continued converging on the solution.
For this experiment, we remained using minimal delays (thousands of a second
magnitude). For this experiment, we only used tournament selection for the
reproduction, on the first configuration running the Life-Cycle on six
processes, two of whom was the Death stage, versus the second configuration
where we reduced the processes to the minimum (five) but increasing the (Death)
goal approval range to 115. We show the summarized results in Table~\ref{tab4}, and
Figure~\ref{fig8} shows their Box and Whisker chart.

>>>>

Experiment 3: The goal of our third experiment was to follow and study the
behavior of the Life-Cycle algorithm that continued converging on the solution.
For this experiment, we remained using minimal delays (thousands of a second
magnitude). For this experiment, we only used tournament selection for the
reproduction, on the first configuration running the Life-Cycle on six
processes, two of whom was the Death process, versus the second configuration
where we reduced the processes to the minimum (five) but increasing the (Death)
goal approval range to 115. We show the summarized results in Table~\ref{tab4},
and Figure~\ref{fig8} shows their Box and Whisker chart.
